Analyzing MLG distribution

### 2017-07-12 doc/RMD/MLG-distribution.Rmd
wrap session info in details tag
add DAPC for region

```{r}
library('tidyverse')
library('poppr')
library('igraph')
library("ggraph")
```

@@

## Session Information

```{r}
options(width = 100)
devtools::session_info()
```

>>>>

```{r load_packages, message = FALSE, warning = FALSE}
library('tidyverse')
library('poppr')
library('igraph')
library("ggraph")
```

@@

### Region Cohesion

Here I am using DAPC to assess how cohesive these artificial regions are.

```{r, region_cohesion}
g11o <- igraph::cluster_optimal(graph11loc$total)
comm <- igraph::communities(g11o)
names(comm) <- c("International", "Costal", "Midwest")
comm
strata(dat11) <- strata(dat11) %>%
  mutate(MLGRegion = case_when(
    .$Region %in% comm$International ~ "International",
    .$Region %in% comm$Costal ~ "Costal",
    .$Region %in% comm$Midwest ~ "Midwest",
    TRUE ~ as.character(.$Region)
  ))

setPop(dat11) <- ~MLGRegion
```

```{r region_dapc}
set.seed(2017-07-12)
reg <- xvalDapc(tab(dat11), pop(dat11), n.rep = 100)
reg$DAPC
scatter(reg$DAPC, col = viridis::viridis(6), bg = "grey90")
ggcompoplot::ggcompoplot(reg$DAPC, dat11, pal = viridis::viridis(6), cols = 2)
reg$DAPC$posterior %>%
  as_tibble() %>%
  bind_cols(data.frame(Population = reg$DAPC$grp)) %>%
  group_by(Population) %>%
  summarize_all(mean) %>%
  gather(assignment, probability, -Population) %>%
  ggplot(aes(x = assignment, y = probability)) +
  geom_segment(aes(xend = assignment, yend = 0)) +
  geom_point(pch = 21, fill = "grey") +
  facet_wrap(~Population) +
  scale_y_continuous(limits = c(0, 1), 
                     minor_breaks = c(seq(0, 1, by = 0.125)), 
                     breaks = c(0, 0.5, 1)) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "top") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  theme(axis.ticks.y = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  theme(panel.grid.major.x = element_line(linetype = 0, color = "grey50")) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(linetype = 3, colour = "grey50")) +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank()) +
  xlab("Population Assignment") +
  ylab("Mean Probability")
```

<details>
<summary>Session Information</summary>

```{r, echo = FALSE}
options(width = 100)
devtools::session_info()
```

</details>
